Learning Discrete Bayesian Networks from Continuous Data

### 2017-05-10 jair_Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
tim edits

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{groupplots}
\usepackage{lscape}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{BOONDOX-cal} % for lowercase caligraphic
\usepackage[font=small,skip=5pt]{caption}
\usepackage[hyphens]{url}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{tabularx}

@@

\author{\name Yi-Chun Chen \email yichunc@stanford.edu \\
	\addr Institute of Computational and Mathematical Engineering, Stanford University,\\
	Stanford, CA  94035 USA
	\AND
	\name Tim A. Wheeler \email wheelert@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA\\
	\AND
	\name Mykel J. Kochenderfer \email mykel@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA}
%\authorrunning{Short form of author list} % if too long for running head

@@

Finding optimal discretization policy to equation \ref{eq:opt_prob} through dynamic programming leads to high computation time when the datasets have more than $100$ variables. The runtime issue becomes more severe if one adapts the MDL approach instead of the proposed Bayesian method in this paper. Thus, approximation approaches are reasonable alternatives, and one possibility is the greedy heuristic \cite{Friedman_1996}. Other approximation methods to dynamic programming are also applicable to solve equation \ref{eq:opt_prob}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{groupplots}
\usepackage{lscape}
\usepackage{siunitx}
\usepackage{booktabs}
% \usepackage{BOONDOX-cal} % for lowercase caligraphic
\usepackage[font=small,skip=5pt]{caption}
\usepackage[hyphens]{url}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{tabularx}

@@

\author{\name Yi-Chun Chen \email yichunc@stanford.edu \\
	\addr Institute of Computational and Mathematical Engineering, Stanford University,\\
	Stanford, CA  94035 USA
	\AND
	\name Tim A. Wheeler \email wheelert@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA
	\AND
	\name Mykel J. Kochenderfer \email mykel@stanford.edu \\
	\addr Department of Aeronautics and Astronautics, Stanford University,\\
	Stanford, CA  94035 USA}
%\authorrunning{Short form of author list} % if too long for running head

@@

Finding optimal discretization policies according to equation~\ref{eq:opt_prob} via dynamic programming requires long computation times when the dataset has more than \num{100} variables.
The runtime for the MDL approach is even more severe.
Approximation approaches are reasonable alternatives for datasets with more variables, including a greedy heuristic~\cite{Friedman_1996}.
Approximations can also be applied during dynamic programming when solving equation~\ref{eq:opt_prob}.
